\documentclass{article}

\usepackage{fullpage}

\title{Recommend Web API Documentation}
\author{David Thompson, thompd10, 400117555}
\date{\today}

\begin{document}

\maketitle

\section*{Overview}

\begin{tabular}{| l | l | l | l |}
  \hline
  \textbf{Routine name} & \textbf{Input} & \textbf{Output} & \textbf{Exceptions} \\
  \hline
  /recommend/restaurant & String & Restaurant & 400, 404 \\
  \hline
  /recommend/search & String, (int) & seq of Restaurant & 400, 404  \\
  \hline
  /recommend/suggest & double, double, seq of String, seq of int, & seq of Restaurant&  400, 404 \\ 
  & (double, int) & & \\
  \hline
\end{tabular}

\newpage

\section*{/recommend/restaurant}
Get the Restaurant with the given ID. The returned restaurant is represented
using JSON.
\subsection*{Example Usage:}
\begin{verbatim}
/recommend/restaurant?id=mlHC2XcU9Bows6cnYEmRgg
\end{verbatim}
\subsection*{Parameters:}
\begin{itemize}
  \item id: The String id of the Restaurant
\end{itemize}
\subsection*{Returns:}
The Restaurant object, represented using JSON.
\subsection*{Exceptions:}
\begin{itemize}
  \item 400: The URL used to call the rountine was malformed
  \item 404: No restaurant with the given ID was found
\end{itemize}

\newpage

\section*{/recommend/search}
Search the database of restaurants with a restaurant whose name begins with
the search query.
\subsection*{Example Usage:}
\begin{verbatim}
/recommend/restaurant?query=Salad+Da&max=3
\end{verbatim}
\subsection*{Parameters:}
\begin{itemize}
  \item query: The start of the name of the restaurant to search for
  \item max: (optional) The maximum number of results to return. The default is 10
\end{itemize}
\subsection*{Returns:}
A newline seperated list of JSON strings, which represent the Restaurant objects
that match the search query.
\subsection*{Exceptions:}
\begin{itemize}
  \item 400: The URL used to call the rountine was malformed
  \item 404: No restaurants whose names begin with the wquery String were found
\end{itemize}

\newpage

\section*{/recommend/suggest}
Recommend restaurants given a list of previous restaurants and ratings, as well
as a few other parameters. Please note the sample syntax for building the lists
in the URL in order to build the lists correctly.
\subsection*{Example Usage:}
Split across multiple lines for readability and in order to fit on the page.
The actual 
\begin{verbatim}
/recommend/suggest?
lat=43.5&long=-79.3
&visited=mlHC2XcU9Bows6cnYEmRgg&stars=4
&visited=LmIGu7WPby4lm8MpELlOMw&stars=2
\end{verbatim}
\subsection*{Parameters:}
\begin{itemize}
  \item lat: The user's latitude in degrees, expressed as a decimal number
  \item long: The user's longitude in degrees, expressed as a decimal number
  \item visited: A list of the Restaurant IDs of where the user has been
  \item stars: A list of the user's ratings of the restaurants they've been to.
  The ratings must be expressed as an integer between 1 and 5 inclusive at both
  endpoints. This integer corresponds to the star rating. The list must be the
  same length as the visited list 
  \item max: (optional) The maximum number of recommendations to return. If no
  value is supplied, the default is 10.
  \item rad: (optional) The cutoff radius for recommendations, as a
  decimal number, in kilometers. Restaurants outside this range will not be
  considered. If no value is supplied, the default value of 100 km is used.
\end{itemize}
\subsection*{Returns:}
A newline seperated list of JSON strings, which represent the Restaurant
objects of the restaurants that are being recommended.
\subsection*{Exceptions:}
\begin{itemize}
  \item 400: The URL used to call the rountine was malformed
  \item 404: No restaurants where found that could be recommended
\end{itemize}

\end{document}